Bayesian Exploration in Deep Reinforcement Learning

### 2022-08-25 papers/CDRL/sample_paper.tex
TEMPORARY DEPLOY COMMIT

\documentclass[twoside]{article}
%\usepackage{aistats2022}
% If your paper is accepted, change the options for the package
% aistats2022 as follows:
%
\usepackage[accepted]{aistats2022}
\usepackage{minted}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

@@

\begin{minted}[mathescape,
  linenos,
  numbersep=5pt,
  gobble=2,
  frame=lines,
  framesep=2mm]{csharp}
string title = "This is a Unicode π in the sky"
/*
Defined as $\pi=\lim_{n\to\infty}\frac{P_n}{d}$ where $P$ is the perimeter
of an $n$-sided regular polygon circumscribing a
circle of diameter $d$.
*/
const double pi = 3.1415926535
\end{minted}

>>>>

\documentclass[twoside]{article}
%\usepackage{aistats2022}
% If your paper is accepted, change the options for the package
% aistats2022 as follows:
%
\usepackage[accepted]{aistats2022}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{xcolor}
%
% This option will print headings for the title of your paper and
% headings for the authors names, plus a copyright note at the end of
% the first column of the first page.

@@

\begin{algorithm}
  \caption{Flow-RL Loss}\label{alg:LTM}
  \textbf{Require:} \(N, v, v^{-1}, \theta, \tilde{\theta}\)\\
  \textbf{input} \(\rvx, a, r, \rvx^\prime, \gamma\)\\
  \hspace*{1em} {\color{gray} \# Take \(N\) samples from the value distribution.}\\
  \hspace*{1em} \textbf{for} \(i = 1 \dots N\)\\
  \hspace*{2em} \(\epsilon_i \sim \N \left(0, I_{\lvert \A \rvert} \right)\)\\
  \hspace*{2em} \textbf{for} \(a^\prime \in \A\)\\
  \hspace*{3em} \(Z_{\tilde{\theta}}(\rvx^\prime, a^\prime)_i \gets v_{\tilde{\theta}}(\epsilon_i; \rvx^\prime)_{a^\prime}\)\\
  \hspace*{2em} \textbf{end}\\
  \hspace*{1em} \textbf{end}\\
  \\\hspace*{1em} {\color{gray} \# Compute greedy next action.}\\
  \hspace*{1em} \(a^* \gets \argmax_{a^\prime} \frac{1}{N} \sum_{i=1}^N Z_{\tilde{\theta}}(\rvx^\prime, a^\prime)_i\)\\
  \\\hspace*{1em} {\color{gray} \# Calculate loss terms for each sample.}\\
  \hspace*{1em} \textbf{for} \(i = 1 \dots N\)\\
  \hspace*{2em} {\color{gray} \# Apply the distributional Bellman operator.}\\
  \hspace*{2em} \(\hat{Z}_{\tilde{\theta}}(\rvx, a)_i \gets r + \gamma Z_{\tilde{\theta}}(\rvx^\prime, a^*)_i\)\\
  \hspace*{2em} {\color{gray} \# Calculate log-probability under \(\N(0,1)\).}\\
  \hspace*{2em} \(\delta_i \gets \frac{1}{2} v_{\theta}^{-1} 
  \left(\hat{Z}_{\tilde{\theta}}(\rvx, a)_i; \rvx \right)^2\)\\
  \hspace*{2em} {\color{gray} \# Calculate log-derivative of \(v^{-1}_\theta\).}\\
  \hspace*{2em} \(\rho_i \gets \log \left\lvert \frac{\partial v_{\theta}^{-1} \left(\hat{Z}_{\tilde{\theta}}(\rvx, a)_i; \rvx \right)}{\hat{Z}_{\tilde{\theta}}(\rvx, a)_i} \right\rvert\)\\
  \hspace*{1em} \textbf{end}\\
  \textbf{output} \(\frac{1}{N}\sum_{i=1}^N \delta_i - \rho_i\)
\end{algorithm}
